Replacing standard galaxy profiles with \\ mixtures of Gaussians

### 2012-10-20 documents/mixtures/mixture_models.tex
abstract tweaks

\begin{abstract}
Exponential and de~Vaucouleurs profiles are simple and successful
models for fitting two-dimensional images of galaxies.  One numerical
issue encountered in this kind of fitting is the pixel rendering and
convolution (or correlation) of the models with the telescope
point-spread function (PSF); these operations are slow, and easy to
get slightly wrong at small radii.  Here we exploit the realization
that these models can be approximated to arbitrary accuracy with a
mixture (linear superposition) of two-dimensional Gaussians.  Mixtures
of Gaussians are fast to render and fast to affine-transform.  Most
importantly, if you have a mixture-of-Gaussian PSF model (which we
advocate), the PSF-convolved, affine-transformed galaxy models are
themselves mixtures of Gaussians and therefore very fast to compute
precisely.  We present worked examples that can be directly used in
image fitting; we are using them ourselves.  We discuss extensions to
S\'ersic models and applications of these ideas to three-dimensional
deprojection.
\end{abstract}

>>>>

\begin{abstract}
Exponential, de~Vaucouleurs, and S\'ersic profiles are simple and
successful models for fitting two-dimensional images of galaxies.  One
numerical issue encountered in this kind of fitting is the pixel
rendering and convolution (or correlation) of the models with the
telescope point-spread function (PSF); these operations are slow, and
easy to get slightly wrong at small radii.  Here we exploit the
realization that these models can be approximated to arbitrary
accuracy with a mixture (linear superposition) of two-dimensional
Gaussians.  Mixtures of Gaussians are fast to render and fast to
affine-transform.  Most importantly, if you have a mixture-of-Gaussian
PSF model (which we advocate), the PSF-convolved, affine-transformed
galaxy models are themselves mixtures of Gaussians and therefore very
fast to compute, integrate, and render precisely.  We present worked
examples that can be directly used in image fitting; we are using them
ourselves.  The mixture profiles we provide can be swapped in to
replace the standard models in any image-fitting code; they ought to
make that code faster at very little cost in accuracy.
\end{abstract}
